Predicting Diabetes Based on Various Factors Using Machine Learning Models

### 2023-12-05 manuscript/manuscript.tex
formatting change
Addition of Confusion Matrix
Title edit

\title{Predicting Diabetes Based on Various Factors Using Decision Trees}
\author{Ashley Merritt\\
    Department of Statistics\\
    University of Connecticut
    }

@@

\section{Methods}
\label{sec:meth}
    Various methods will be used to complete the statistical analysis necessary for this project. I will begin by exploring basic 
    descriptive statistics to gain an understanding of my data set. I will then begin to create my model for my decision tree by
    splitting the data into a test and training set. The training set will encompass 80 percent of the data whereas the test set will
    only have 20 percent. After creating these two sets we will now be ready to build the model, this will be done by using the rpart
    function in R, where method will be 'class' as this is a binary model. We will then see in Figure~\ref{tab:structure} the structure
    of the decision tree created. Looking at the leftmost path in the decision tree we can see that at the top the outcome was 0 meaning 
    that the patient did not have diabetes 35 percent of the time. Moving down to the next node, we can see that 68 percent of patients with
    glucose level less than 128, did not have diabetes 19 percent of the time. To finish this path, 61 percent of the time if the patient was
    older than 29 years old, then 8 percent of the time the patient had diabetes. The rest of the structure is similar but with different 
    values and predictors.

@@

>>>>

\title{Predicting Diabetes Based on Various Factors Using Machine Learning Models}
\author{Ashley Merritt\\
    Department of Statistics\\
    University of Connecticut
    }

@@

\section{Methods}
\label{sec:meth}
    Various methods will be used to complete the statistical analysis necessary for this project. I will begin by exploring basic 
    descriptive statistics to gain an understanding of my data set. I will then begin to create my model for my decision tree by
    splitting the data into a test and training set. The training set will encompass 80 percent of the data whereas the test set will
    only have 20 percent. After creating these two sets we will now be ready to build the model, this will be done by using the rpart
    function in R, where method will be 'class' as this is a binary model. We will then see in Figure~\ref{fig:structure} the structure
    of the decision tree created. Looking at the leftmost path in the decision tree we can see that at the top the outcome was 0 meaning 
    that the patient did not have diabetes 35 percent of the time. Moving down to the next node, we can see that 68 percent of patients with
    glucose level less than 128, did not have diabetes 19 percent of the time. To finish this path, 61 percent of the time if the patient was
    older than 29 years old, then 8 percent of the time the patient had diabetes. The rest of the structure is similar but with different 
    values and predictors.

@@

\begin{table}[ht]
  \centering
  \caption{Confusion Matrix} 
  \begin{tabular}{rrr}
    \toprule
    & 0 & 1 \\ 
    \midrule
  0 & 318 & 47 \\ 
    1 & 53 & 136 \\ 
    \bottomrule
  \end{tabular}
  \label{tab:conf_matrix}
  \end{table}
